---
title: " R package making"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ R package making}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(VINH4753SPR25)
```


# introduction

# dataset 

Fire dataset. the dat agiven is taken from the test books. the data is includes in the pacakge. and can be called directly if the the libary is called. Or, user can specify specific package as fire

```{R}
# this approach
head(fire)
# or print full
VINH4753SPR25::fire
```


## dotplot color

```{r}
# this is an example indicate a red plot mean outliers
dotplotcolor(c(1,2,3,4,5,6,7,8,9,1,1,11,12,18,-8,100))
# this will indicate a blue  meaning possible ouliers
dotplotcolor(c(0.000001,0.02,0.0123,0.01234,0.0235,0.0156,0.022,0.044))

```

## myboot2

we denote that $\mu=10$ and $\sigma=12$. a is a user input region from 0 to y value.

```{r}
# lab 06
myncurve(mu=10,sigma=12,a= 20)

```


## mycurve

First of all we need to set random number  as 5. rnorm will the number to generate num.
take input how many iterations, density num, calculate as mean, conf interval, extra such as label x axis and color.

```{r}
set.seed(5); testing01=rnorm(10,mean=12,sd=8)
# lab 10
myboot2(iter=12500, x=testing01, fun = "mean",alpha=0.25,xlab="mean",col="tomato3")

```
## mysamplefunction

this will take input n sample size. iter meaning how many plot do we need. finially time is the 
This functions is randomize sample

```{r}

myf(123, iter = 8, time =0.75)

```



